Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-01-05 paper.tex
Added description about handling of non-linear and non-convex optimization problems

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints;
	\item handling of concurrent software;
	\item platform restrictions;
	\item legacy designs; and %, which are usually developed with low-level languages.
	\item support to different programming languages and interfaces;
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. In particular, software developed for that type of embedded systems has been extensively tested and verified, and also optimized for efficiency over years of development. Therefore, when a new product is derived from a given platform, a lot of legacy code is usually reused for improving development time and code quality. Finally, the last one is related to the evolution of development processes and technologies, which may delay the application of suitable verification approaches.

@@

%--------------------------------------
\section{Current Achievements and Future Trends}
\label{achievements}
%--------------------------------------

@@

{\textbf{(RP6)} State-of-the-art synthesis approaches for embedded (control) systems typically disregard the platform in which the embedded system software operates and restrict itself to generate code that do not take into account FWL effects. The synthesized system, however, must include the physical plant to avoid serious system's malfunctioning (or even a catastrophe) due to the embedded (control) software, {\it e.g.}, the Mars Polar Lander did not account for leg compressions prior to landing~\cite{Jackson16}. Research in this direction has made some progress to design, implement, and evaluate an automated approach for generating correct-by-construction digital controllers that is based on state-of-the-art inductive synthesis techniques~\cite{Abate17}. However, there is still little evidence whether that approach can scale for larger systems modeled by other types of representations ({\it e.g.}, state-space). Another research direction for synthesizers is to generate code for UAV trajectory and mission planning by taking into account system's dynamics and nonholonomic constraints~\cite{Araujo16}.

@@

%1
\bibitem{Kopetz11}
H.~Kopetz:
\newblock {\em Real-Time Systems - Design Principles for Distributed Embedded Applications}.
\newblock Real-Time Systems Series, Springer, ISBN 978-1-4419-8236-0, pp. 1--376, 2011.

%2
\bibitem{xu15}
Xua X., Jiaa H., Wanga D., Yub D., Chiangc H.:
\newblock {\em Hierarchical energy management system for multi-source multi-product microgrids}
\newblock In: Renewable Energy, v. 78, pp. 621--630, 2015.

%3
\bibitem{leeCPS}
Lee E.:
\newblock {\em Cyber-physical Systems: Design Challenges.} 
\newblock In: International Symposium on Object Oriented Real-Time Distributed Computing, pp. 363--369, 2008.

%4
\bibitem{leeCPS2}
Lee E.:
\newblock {\em The Past, Present and Future of Cyber-Physical Systems: A Focus on Models}. 
\newblock In: Sensors 15(3): pp. 4837--4869, 2015.

%5
\bibitem{groza2015formal}
Groza A., Letia I., Goron A., Zaporojan S.: 
\newblock {\em A formal approach for identifying assurance deficits in unmanned aerial vehicle software}
\newblock In: Progress in Systems Engineering, Springer, pp. 233--239, 2015.

%6
\bibitem{Cordeiro09}
Cordeiro L., Fischer B., Chen H., Marques-Silva J.:
\newblock {\em Semiformal Verification of Embedded Software in Medical Devices Considering Stringent Hardware Constraints.} 
\newblock In: International Conference on Embedded Software and Systems, pp. 396--403, 2009.

%7
\bibitem{munir}
Munir S., Stankovic J. A., Liang C.-J. M., Lin S.:
\newblock {\em Cyber Physical System Challenges for Human-in-the-Loop Control}. 
\newblock In: 8th International Workshop on Feedback Computing, pp. 1--4, 2013.

%8
\bibitem{Abate17}
Abate A., Bessa I., Cattaruzza D., Cordeiro L., David C., Kesseli P., Kroening D.:
\newblock {\em Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants}.
\newblock In: 20th ACM International Conference on Hybrid Systems: Computation and Control, 2017 (to appear).

%9
\bibitem{Kroening15}
Kroening D., Liang L., Melham T., Schrammel P., Tautschnig M.:
\newblock {\em Effective Verification of Low-Level Software with Nested Interrupts}. 
\newblock In: Design, Automation and Test in Europe, pp. 229--234, 2015.

%10
\bibitem{Biere99}
Biere A., Cimatti A., Clarke E., Zhu Y.:
\newblock {\em Symbolic Model Checking without BDDs}. 
\newblock In: Tools and Algorithms for Construction and Analysis of Systems, LNCS 1579, pp. 193--207, 1999.

%11
\bibitem{handbook09}
Biere A., Heule M., van Maaren H., Walsh T., eds.:
\newblock {\em Handbook of Satisfiability}.
\newblock Volume 185 of Frontiers in Artificial Intelligence and Applications., {IOS} Press, 2009.

%12
\bibitem{BarrettSST09}
Barrett C., Sebastiani R., Seshia S.A., Tinelli C.:
\newblock {\em Satisfiability Modulo Theories}. 
\newblock In: Volume 185 of Frontiers in Artificial Intelligence and Applications. IOS Press, pp. 825--885, 2009.

%13
\bibitem{Armando06}
Armando A., Mantovani J., Platania L.:
\newblock {\em Bounded Model Checking of Software Using SMT Solvers Instead of SAT Solvers}. 
\newblock In: {SPIN} Workshop on Model Checking Software, LNCS 3925, pp. 146-162, 2006.

%14
\bibitem{Clarke04}
Clarke E., Kroening D., Lerda F.:
\newblock {\em A Tool for Checking {ANSI-C} Programs.}
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems. LNCS 2988, Springer Berlin Heidelberg, pp. 168--176, 2004.

%15
\bibitem{MerzFS12}
Merz F., Falke S., Sinz C.:
\newblock {\em {LLBMC}: Bounded Model Checking of {C} and {C++} Programs using a Compiler {IR}.}
\newblock In: International Conference on Verified Software: Theories, Tools, Experiments. LNCS 7152, pp. 146--161, 2012.

%16
\bibitem{CordeiroF11}
Cordeiro L., Fischer B.:
\newblock {\em Verifying Multi-threaded Software using {SMT}-based Context-Bounded Model Checking.}
\newblock In: International Conference on Software Engineering. pp. 331--340, 2011.

%17
\bibitem{Ivancic05}
Ivanicic F., Shlyakhter I., Gupta A., Ganai, M.K.:
\newblock {\em Model Checking {C} Programs using {F-Soft}.}
\newblock In: International Conference on Computer Design: VLSI in Computers and Processors, pp. 297--308, 2005.

%18
\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software}.
\newblock {IEEE} Trans. Software Eng. \textbf{38}(4), pp. 957--974, 2012.

%19
\bibitem{EenS03}
E{\'{e}}n, N., S{\"{o}}rensson, N.:
\newblock {\em Temporal Induction by Incremental {SAT} Solving.}
\newblock Electronic Notes in Theoretical Computer Science \textbf{89}(4), pp. 543 -- 560, 2003.

%20
\bibitem{Sheera00}
Sheeran M., Singh S., St{\aa}lmarck G.:
\newblock {\em Checking Safety Properties using Induction and a {SAT}-solver.}
\newblock In: International Conference on Formal Methods in Computer-Aided Design. Springer-Verlag, pp. 108--125, 2000.

%21
\bibitem{Bradley07}
Bradley A., Manna Z.:
\newblock {\em The calculus of computation - decision procedures with applications to verification}. 
\newblock In: Springer, pp. I-XV, pp. 1--366, 2007.

%22
\bibitem{pips:2013}
ParisTech M.:
\newblock {\em PIPS: Automatic Parallelizer and Code Transformation Framework.} 
\newblock Accessed 21 February 2016

%23
\bibitem{Henry:2012}
Henry J., Monniaux D., Moy M.: 
\newblock {\em PAGAI: A Path Sensitive Static Analyser.} 
\newblock In: Electronic Notes in Theoretical Computer Science, pp. 15--25, 2012.

%24
\bibitem{Gadelha15}
Gadelha M., Ismail H., Cordeiro L.:
\newblock {\em Handling Loops in Bounded Model Checking of C Programs via \textit{k}-Induction.}
\newblock In: International Journal on Software Tools for Technology Transfer (to appear), 2015.
\newblock http://dx.doi.org/10.1007/s10009-015-0407-9

%25
\bibitem{Beyer15}
Beyer D., Dangl M., Wendler P.:
\newblock {\em Boosting \textit{k}-Induction with Continuously-Refined Invariants.}
\newblock In: International Conference on Computer-Aided Verification, LNCS 9206, pp. 622--640, 2015.

%26
\bibitem{Brain15}
Brain M., Joshi S., Kroening D., Schrammel P.:
\newblock {\em Safety Verification and Refutation by k-Invariants and \textit{k}-Induction.}
\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.

%27
\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em Model Checking Embedded C Software using \textit{k}-Induction and Invariants.}
\newblock In: V Brazilian Symposium on Computing Systems Engineering, pp. 90--95, 2015.

%28
\bibitem{Kinductor}
Donaldson A., Haller L., Kroening D., R{\"{u}}mmer, P.:
\newblock {\em Software Verification using \textit{k}-Induction.}
\newblock In: International Symposium on Static Analysis. LNCS 6887, pp. 351--368, 2011.

%29
\bibitem{Rocha17}
Rocha, W., Rocha, H., Ismail H., Cordeiro, L., Fischer, B.:
\newblock {\em DepthK: A \textit{k}-Induction Verifier Based on Invariant Inference for C Programs}. 
\newblock In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems, 2017 (to appear).

%30
\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {SCRATCH}: A Tool for Automatic Analysis of {DMA} Races.}
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

%31
\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em Induction-based Formal Verification of {SystemC TLM} Designs.}
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

%32
\bibitem{Alur13}
Alur R., Bod\'{\i}k R., Juniwal G., Martin M., Raghothaman M., Seshia S., Singh R., Solar-Lezama A., Torlak E., Udupa A.:
\newblock {\em Syntax-guided synthesis}. 
\newblock In: Formal Methods in Computer-Aided Design, pp. 1--8, 2013.

%33
\bibitem{sketch}
A.~Solar-Lezama.
\newblock {\em Program sketching}.
\newblock In: International Journal on Software Tools for Technology Transfer, 15(5-6):475--495, 2013.

%34
\bibitem{David15}
C.~David, D.~Kroening, and M.~Lewis.
\newblock {\em Using program synthesis for program analysis}.
\newblock In: Logic for Programming, Artificial Intelligence, and Reasoning, LNCS 9450, pp. 483--498, 2015.

%35
\bibitem{Sharma14}
R.~Sharma and A.~Aiken.
\newblock {\em From invariant checking to invariant inference using randomized search}.
\newblock In: Computer Aided Verification, LNCS 8559, pp. 88--105, 2014.

%36
\bibitem{dsv_spin2015}
Ismail H., Bessa I., Cordeiro L., Lima Filho E., Chaves Filho J.:
\newblock {\em DSVerifier: A Bounded Model Checking Tool for Digital Systems}. 
\newblock In: International SPIN Symposium on Model Checking of Software, LNCS 9232, pp. 126--131, 2015.

%37
\bibitem{Monteiro16}
F.~Monteiro:
\newblock {\em Bounded model checking of state-space digital systems: the impact of finite word-length effects on the implementation of fixed-point digital controllers based on state-space modeling}. 
\newblock In: 24th {ACM} {SIGSOFT} International Symposium on Foundations of Software Engineering, pp. 1151--1153, 2016.

%38
\bibitem{Bessa17}
Bessa, I., Ismail, H., Palhares, R., Cordeiro, L., Chaves Filho, J.:
\newblock {\em Formal Non-Fragile Stability Verification of Digital Control Systems with Uncertainty}. 
\newblock In: IEEE Transactions on Computers, 2017 (to appear).

%39
\bibitem{Behrend15}
Behrend J., Lettnin D., Gruenhage A., Ruf J., Kropf T., Rosenstiel W.:
\newblock {\em Scalable and Optimized Hybrid Verification of Embedded Software}. 
\newblock In: J. Electronic Testing 31(2): pp. 151--166, 2015.

%40
\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
\newblock {\em Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

%41
\bibitem{Beyer14}
D.~Beyer 
\newblock {Status report on software verification - (competition summary {SV-COMP})}. 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.

%42
\bibitem{BeyerSVCOMP15}
D.~Beyer:
\newblock {\em Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).} 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.

%43
\bibitem{Inverso14}
Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
\newblock {\em Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}
\newblock In: International Conference on Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.

%44
\bibitem{ECBS13}
Ramalho M., Lopes M., Sousa F., Marques H., Cordeiro L., Fischer B.:
\newblock {\em {SMT-Based Bounded Model Checking of C++ Programs} }.
\newblock In: International Conference on Engineering of Computer-Based Systems, pp. 147--156, 2013.

%45
\bibitem{Pereira15}
Pereira P.  Albuquerque H., Marques H., Silva I., Carvalho C., Santos V., Ferreira R., Cordeiro L.: 
\newblock {\em Verifying CUDA Programs using SMT-Based Context-Bounded Model Checking.} 
\newblock In: ACM Symposium on Applied Computing, Software Verification and Testing Track, pp. 1648-1653, 2016.

%46
\bibitem{Sousa15}
Sousa F., Cordeiro L., Lima Filho E.: 
\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.

%47
\bibitem{morse15}
J.~Morse.
\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
\newblock {University of Southampton, PhD Thesis}, 2015.

%48
\bibitem{civl15}
Zheng M, Rogers M, Luo Z, Dwyer M, Siegel S.
\newblock {\em{{CIVL}: Formal Verification of Parallel Programs}}.
\newblock In: International Conference on Automated Software Engineering, pp. 830--835, 2015.

%49
\bibitem{Grumberg05}
Grumberg O., Lerda F., Strichman O., Theobald M.:
\newblock {\em { Proof-guided underapproximation-widening for multi-process systems.}} 
\newblock In: Symposium on Principles of Programming Languages, pp. 122--131, 2005.

%50
\bibitem{McMillan11}
K.~McMillan:
\newblock {\em {Widening and Interpolation.}} 
\newblock In: International Symposium on Static Analysis, LCNS 6887, pp. 1, 2011.

%51
\bibitem{esbmc_controller}
Bessa I., Abreu R., Cordeiro L., Filho J.:
\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers}.}
\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.

%52
\bibitem{esbmc_filter}
Abreu R., Cordeiro L., Filho E.:
\newblock {\em {Verifying Fixed-Point Digital Filters using SMT-Based Bounded Model Checking}.}
\newblock In: XXXI Brazilian Symposium on Telecommunications, 2013.
\newblock http://dx.doi.org/10.14209/sbrt.2013.57

%53
\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.

>>>>

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints.
	\item handling of concurrent software.
	\item platform restrictions.
	\item legacy designs. %, which are usually developed with low-level languages.
	\item support to different programming languages and interfaces.
	\item handling of non-linear and non-convex optimization problems.
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. In particular, software developed for that type of embedded systems has been extensively tested and verified, and also optimized for efficiency over years of development. Therefore, when a new product is derived from a given platform, a lot of legacy code is usually reused for improving development time and code quality. The fifth aspect is related to the evolution of development processes and technologies, which may delay the application of suitable verification and synthesis approaches if verifiers and synthesizers do not support different programming languages and interfaces. Finally, the last one is related to the widespread use of embedded systems in autonomous vehicles navigation systems~\cite{Adouane16}, which demand optimization solving during their execution for a wide range of functions, including non-linear and non-convex problems using fixed- and floating-point arithmetic.

@@

%--------------------------------------
\section{Current Achievements and \\ Future Trends}
\label{achievements}
%--------------------------------------

@@

{\textbf{(RP6)} State-of-the-art synthesis approaches for embedded (control) systems typically disregard the platform in which the embedded system software operates and restrict itself to generate code that do not take into account FWL effects. The synthesized system, however, must include the physical plant to avoid serious system's malfunctioning (or even a catastrophe) due to the embedded (control) software, {\it e.g.}, the Mars Polar Lander did not account for leg compressions prior to landing~\cite{Jackson16}. Research in this direction has made some progress to design, implement, and evaluate an automated approach for generating correct-by-construction digital controllers that is based on state-of-the-art inductive synthesis techniques~\cite{Abate17}. However, there is still little evidence whether that approach can scale for larger systems modeled by other types of representations ({\it e.g.}, state-space). In addition to that, another research direction for synthesizers is to generate code for UAV trajectory and mission planning by taking into account system's dynamics and nonholonomic constraints~\cite{Araujo16}. As a consequence, verifiers and synthesizers need to handle a wide range of functions, including non-linear and non-convex optimization problems based on both fixed- and floating-point arithmetic.

@@

%1
\bibitem{Kopetz11}
H.~Kopetz:
\newblock {\em {Real-Time Systems - Design Principles for Distributed Embedded Applications}}.
\newblock Real-Time Systems Series, Springer, ISBN 978-1-4419-8236-0, pp. 1--376, 2011.

%2
\bibitem{xu15}
Xua X., Jiaa H., Wanga D., Yub D., Chiangc H.:
\newblock {\em {Hierarchical energy management system for multi-source multi-product microgrids}}.
\newblock In: Renewable Energy, v. 78, pp. 621--630, 2015.

%3
\bibitem{leeCPS}
Lee E.:
\newblock {\em {Cyber-physical Systems: Design Challenges}}.
\newblock In: International Symposium on Object Oriented Real-Time Distributed Computing, pp. 363--369, 2008.

%4
\bibitem{leeCPS2}
Lee E.:
\newblock {\em {The Past, Present and Future of Cyber-Physical Systems: A Focus on Models}}. 
\newblock In: Sensors 15(3): pp. 4837--4869, 2015.

%5
\bibitem{groza2015formal}
Groza A., Letia I., Goron A., Zaporojan S.: 
\newblock {\em {A formal approach for identifying assurance deficits in unmanned aerial vehicle software}}.
\newblock In: Progress in Systems Engineering, Springer, pp. 233--239, 2015.

%6
\bibitem{Cordeiro09}
Cordeiro L., Fischer B., Chen H., Marques-Silva J.:
\newblock {\em {Semiformal Verification of Embedded Software in Medical Devices Considering Stringent Hardware Constraints}}.
\newblock In: International Conference on Embedded Software and Systems, pp. 396--403, 2009.

%7
\bibitem{munir}
Munir S., Stankovic J. A., Liang C.-J. M., Lin S.:
\newblock {\em {Cyber Physical System Challenges for Human-in-the-Loop Control}}. 
\newblock In: 8th International Workshop on Feedback Computing, pp. 1--4, 2013.

%8
\bibitem{Abate17}
Abate A., Bessa I., Cattaruzza D., Cordeiro L., David C., Kesseli P., Kroening D.:
\newblock {\em {Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants}}.
\newblock In: 20th ACM International Conference on Hybrid Systems: Computation and Control, 2017 (to appear).

%9
\bibitem{Kroening15}
Kroening D., Liang L., Melham T., Schrammel P., Tautschnig M.:
\newblock {\em {Effective Verification of Low-Level Software with Nested Interrupts}}. 
\newblock In: Design, Automation and Test in Europe, pp. 229--234, 2015.

%10
\bibitem{Biere99}
Biere A., Cimatti A., Clarke E., Zhu Y.:
\newblock {\em {Symbolic Model Checking without BDDs}}. 
\newblock In: Tools and Algorithms for Construction and Analysis of Systems, LNCS 1579, pp. 193--207, 1999.

%11
\bibitem{handbook09}
Biere A., Heule M., van Maaren H., Walsh T., eds.:
\newblock {\em {Handbook of Satisfiability}}.
\newblock Volume 185 of Frontiers in Artificial Intelligence and Applications., {IOS} Press, 2009.

%12
\bibitem{BarrettSST09}
Barrett C., Sebastiani R., Seshia S.A., Tinelli C.:
\newblock {\em {Satisfiability Modulo Theories}}. 
\newblock In: Volume 185 of Frontiers in Artificial Intelligence and Applications. IOS Press, pp. 825--885, 2009.

%13
\bibitem{Armando06}
Armando A., Mantovani J., Platania L.:
\newblock {\em {Bounded Model Checking of Software Using SMT Solvers Instead of SAT Solvers}}. 
\newblock In: {SPIN} Workshop on Model Checking Software, LNCS 3925, pp. 146-162, 2006.

%14
\bibitem{Clarke04}
Clarke E., Kroening D., Lerda F.:
\newblock {\em {A Tool for Checking {ANSI-C} Programs}}.
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems. LNCS 2988, Springer Berlin Heidelberg, pp. 168--176, 2004.

%15
\bibitem{MerzFS12}
Merz F., Falke S., Sinz C.:
\newblock {\em {{LLBMC}: Bounded Model Checking of {C} and {C++} Programs using a Compiler {IR}}}.
\newblock In: International Conference on Verified Software: Theories, Tools, Experiments. LNCS 7152, pp. 146--161, 2012.

%16
\bibitem{CordeiroF11}
Cordeiro L., Fischer B.:
\newblock {\em {Verifying Multi-threaded Software using {SMT}-based Context-Bounded Model Checking}}.
\newblock In: International Conference on Software Engineering. pp. 331--340, 2011.

%17
\bibitem{Ivancic05}
Ivanicic F., Shlyakhter I., Gupta A., Ganai, M.K.:
\newblock {\em {Model Checking {C} Programs using {F-Soft}}}.
\newblock In: International Conference on Computer Design: VLSI in Computers and Processors, pp. 297--308, 2005.

%18
\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {{SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software}}.
\newblock {IEEE} Trans. Software Eng. 38(4), pp. 957--974, 2012.

%19
\bibitem{EenS03}
E{\'{e}}n, N., S{\"{o}}rensson, N.:
\newblock {\em {Temporal Induction by Incremental {SAT} Solving}}.
\newblock Electronic Notes in Theoretical Computer Science 89(4), pp. 543 -- 560, 2003.

%20
\bibitem{Sheera00}
Sheeran M., Singh S., St{\aa}lmarck G.:
\newblock {\em {Checking Safety Properties using Induction and a {SAT}-solver}}.
\newblock In: International Conference on Formal Methods in Computer-Aided Design. Springer-Verlag, pp. 108--125, 2000.

%21
\bibitem{Bradley07}
Bradley A., Manna Z.:
\newblock {\em {The calculus of computation - decision procedures with applications to verification}}. 
\newblock In: Springer, pp. I-XV, pp. 1--366, 2007.

%22
\bibitem{pips:2013}
ParisTech M.:
\newblock {\em {PIPS: Automatic Parallelizer and Code Transformation Framework}}. 
\newblock Accessed 21 February 2016

%23
\bibitem{Henry:2012}
Henry J., Monniaux D., Moy M.: 
\newblock {\em {PAGAI: A Path Sensitive Static Analyser}}. 
\newblock In: Electronic Notes in Theoretical Computer Science, pp. 15--25, 2012.

%24
\bibitem{Gadelha15}
Gadelha M., Ismail H., Cordeiro L.:
\newblock {\em {Handling Loops in Bounded Model Checking of C Programs via \textit{k}-Induction}}.
\newblock In: International Journal on Software Tools for Technology Transfer (to appear), 2015.
\newblock http://dx.doi.org/10.1007/s10009-015-0407-9

%25
\bibitem{Beyer15}
Beyer D., Dangl M., Wendler P.:
\newblock {\em {Boosting \textit{k}-Induction with Continuously-Refined Invariants}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 9206, pp. 622--640, 2015.

%26
\bibitem{Brain15}
Brain M., Joshi S., Kroening D., Schrammel P.:
\newblock {\em {Safety Verification and Refutation by k-Invariants and \textit{k}-Induction}}.
\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.

%27
\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em {Model Checking Embedded C Software using \textit{k}-Induction and Invariants}}.
\newblock In: V Brazilian Symposium on Computing Systems Engineering, pp. 90--95, 2015.

%28
\bibitem{Kinductor}
Donaldson A., Haller L., Kroening D., R{\"{u}}mmer, P.:
\newblock {\em {Software Verification using \textit{k}-Induction}}.
\newblock In: International Symposium on Static Analysis. LNCS 6887, pp. 351--368, 2011.

%29
\bibitem{Rocha17}
Rocha, W., Rocha, H., Ismail H., Cordeiro, L., Fischer, B.:
\newblock {\em {DepthK: A \textit{k}-Induction Verifier Based on Invariant Inference for C Programs}}. 
\newblock In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems, 2017 (to appear).

%30
\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {{SCRATCH}: A Tool for Automatic Analysis of {DMA} Races}}.
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

%31
\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em {Induction-based Formal Verification of {SystemC TLM} Designs}}.
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

%32
\bibitem{Alur13}
Alur R., Bod\'{\i}k R., Juniwal G., Martin M., Raghothaman M., Seshia S., Singh R., Solar-Lezama A., Torlak E., Udupa A.:
\newblock {\em {Syntax-guided synthesis}}. 
\newblock In: Formal Methods in Computer-Aided Design, pp. 1--8, 2013.

%33
\bibitem{sketch}
A.~Solar-Lezama.
\newblock {\em {Program sketching}}.
\newblock In: International Journal on Software Tools for Technology Transfer, 15(5-6):475--495, 2013.

%34
\bibitem{David15}
C.~David, D.~Kroening, and M.~Lewis.
\newblock {\em {Using program synthesis for program analysis}}.
\newblock In: Logic for Programming, Artificial Intelligence, and Reasoning, LNCS 9450, pp. 483--498, 2015.

%35
\bibitem{Sharma14}
R.~Sharma and A.~Aiken.
\newblock {\em {From invariant checking to invariant inference using randomized search}}.
\newblock In: Computer Aided Verification, LNCS 8559, pp. 88--105, 2014.

%36
\bibitem{dsv_spin2015}
Ismail H., Bessa I., Cordeiro L., Lima Filho E., Chaves Filho J.:
\newblock {\em {DSVerifier: A Bounded Model Checking Tool for Digital Systems}}. 
\newblock In: International SPIN Symposium on Model Checking of Software, LNCS 9232, pp. 126--131, 2015.

%37
\bibitem{Monteiro16}
F.~Monteiro:
\newblock {\em {Bounded model checking of state-space digital systems: the impact of finite word-length effects on the implementation of fixed-point digital controllers based on state-space modeling}}. 
\newblock In: 24th {ACM} {SIGSOFT} International Symposium on Foundations of Software Engineering, pp. 1151--1153, 2016.

%38
\bibitem{Bessa17}
Bessa, I., Ismail, H., Palhares, R., Cordeiro, L., Chaves Filho, J.:
\newblock {\em {Formal Non-Fragile Stability Verification of Digital Control Systems with Uncertainty}}. 
\newblock In: IEEE Transactions on Computers, 2017 (to appear).

%39
\bibitem{Behrend15}
Behrend J., Lettnin D., Gruenhage A., Ruf J., Kropf T., Rosenstiel W.:
\newblock {\em {Scalable and Optimized Hybrid Verification of Embedded Software}}. 
\newblock In: J. Electronic Testing 31(2): pp. 151--166, 2015.

%40
\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
\newblock {\em {Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

%41
\bibitem{Adouane16}
Vilca J., Adouane L., Mezouar Y.:
\newblock {\em {Optimal Multi-Criteria Waypoint Selection for Autonomous Vehicle Navigation in Structured Environment}}. 
\newblock In: Journal of Intelligent and Robotic Systems 82(2): pp. 301--324, 2016.

%42
\bibitem{Beyer14}
D.~Beyer 
\newblock {\em {Status report on software verification - (competition summary {SV-COMP})}}. 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.

%43
\bibitem{BeyerSVCOMP15}
D.~Beyer:
\newblock {\em {Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).}} 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.

%44
\bibitem{Inverso14}
Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
\newblock {\em {Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}}
\newblock In: International Conference on Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.

%45
\bibitem{ECBS13}
Ramalho M., Lopes M., Sousa F., Marques H., Cordeiro L., Fischer B.:
\newblock {\em {SMT-Based Bounded Model Checking of C++ Programs} }.
\newblock In: International Conference on Engineering of Computer-Based Systems, pp. 147--156, 2013.

%46
\bibitem{Pereira15}
Pereira P.  Albuquerque H., Marques H., Silva I., Carvalho C., Santos V., Ferreira R., Cordeiro L.: 
\newblock {\em {Verifying CUDA Programs using SMT-Based Context-Bounded Model Checking}}.
\newblock In: ACM Symposium on Applied Computing, Software Verification and Testing Track, pp. 1648-1653, 2016.

%47
\bibitem{Sousa15}
Sousa F., Cordeiro L., Lima Filho E.: 
\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.

%48
\bibitem{morse15}
J.~Morse.
\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
\newblock {University of Southampton, PhD Thesis}, 2015.

%49
\bibitem{civl15}
Zheng M, Rogers M, Luo Z, Dwyer M, Siegel S.
\newblock {\em{{CIVL}: Formal Verification of Parallel Programs}}.
\newblock In: International Conference on Automated Software Engineering, pp. 830--835, 2015.

%50
\bibitem{Grumberg05}
Grumberg O., Lerda F., Strichman O., Theobald M.:
\newblock {\em { Proof-guided underapproximation-widening for multi-process systems.}} 
\newblock In: Symposium on Principles of Programming Languages, pp. 122--131, 2005.

%51
\bibitem{McMillan11}
K.~McMillan:
\newblock {\em {Widening and Interpolation.}} 
\newblock In: International Symposium on Static Analysis, LCNS 6887, pp. 1, 2011.

%52
\bibitem{esbmc_controller}
Bessa I., Abreu R., Cordeiro L., Filho J.:
\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers}.}
\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.

%53
\bibitem{esbmc_filter}
Abreu R., Cordeiro L., Filho E.:
\newblock {\em {Verifying Fixed-Point Digital Filters using SMT-Based Bounded Model Checking}.}
\newblock In: XXXI Brazilian Symposium on Telecommunications, 2013.
\newblock http://dx.doi.org/10.14209/sbrt.2013.57

%54
\bibitem{JMorse15}
Morse J., Cordeiro L., Nicole D., Fischer B.:
\newblock {\em {Model Checking LTL Properties over ANSI-C Programs with Bounded Traces.}} 
\newblock In: Software and System Modeling 14(1): pp. 65--81, 2015.
